%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior AI \& Data Platform Engineer} % Job title
    {JOE \& THE JUICE} % Organization
    {Copenhagen, Denmark} % Location
    {Oct. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected enterprise data platform from the ground up, enabling IPO-ready financial reporting for 2028 while powering global store expansion (400 → 1,000+). Delivered scalable ML foundations and self-service analytics through LLM-enabled semantic models - dbt MCP semantic layer.}
        \item {Reduced \textbf{dbt} runtime for main data mart from \textbf{1.5 hours to 3 minutes}, unlocking near real-time analytics.}
        \item {Implemented automated data ingestion via Snowpipe, S3, API webhooks, and \textbf{Fivetran} (migrating to Estuary), ensuring scalable pipelines.}
        \item {Delivered ML-ready architecture with \textbf{MLOps} framework (dbt + Snowflake + Python), improving demand forecasting accuracy by \textbf{50\%} and generating \textbf{1M+ DKK} annual savings.}
        \item {Introduced self-service analytics through \textbf{dbt} MCP semantic layer integrated with LLMs, enabling natural language queries across business teams.}
        \item {Established comprehensive \textbf{role-based access control (RBAC)} system using \textbf{Terraform} and Azure AD, distinguishing access levels for developers, business analysts, etc.}
        \item {Mentored junior engineers and established governance frameworks to standardize data modeling and architecture practices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant - Data Engineer} % Job title
    {Netlight} % Organization
    {Copenhagen, Denmark} % Location
    {Sep. 2023 - Oct. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated legacy on-prem SQL systems to \textbf{Snowflake}, delivering a self-service data mesh that enabled independent data product development.}
        \item {Automated ESG reporting workflows, saving \textbf{2 FTE} annually, and developed emissions targeting tools that passed Big Four audit scrutiny.}
        \item {Enabled cross-domain data access and analytics using Azure, \textbf{dbt}, Python, \textbf{Terraform}, Kubernetes, fostering a data-driven culture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant - Data Engineer / Data Scientist} % Job title
    {ADC (Amsterdam Data Collective)} % Organization
    {Copenhagen, Denmark} % Location
    {Aug. 2021 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed metadata management platform for pharmaceutical clinical trials using \textbf{AWS, Elasticsearch, and FastAPI}, streamlining regulatory data retrieval.}
        \item {Engineered proof-of-concept clinical trial data platform with \textbf{AWS Glue, S3, CDK, and Step Functions}, enabling scalable data processing.}
        \item {Modernized production planning applications by migrating to \textbf{AWS Serverless (Lambda, Fargate)}, reducing infrastructure overhead and improving scalability.}
        \item {Built ML models with \textbf{Azure, MLFlow, and XGBoost} to predict product returns, reducing waste and improving customer satisfaction for a medtech client.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist (Part-time Student)} % Job title
    {Novo Nordisk} % Organization
    {Hillerød, Denmark} % Location
    {Apr. 2019 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed ML models for predictive maintenance and image classification in pharma manufacturing, reducing downtime and improving quality assurance.}
        \item {Built \textbf{AWS}-based ML infrastructure with \textbf{S3, Lambda, and EC2}, enabling scalable data pipelines for production environments.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
